Hydras, Ordinals \& Co. \\ A library in Coq of entertaining formal mathematics

### 2021-09-30 doc/JFLA2022/paper.tex
First stab at presenting Coq-community.

>>>>

\emph{Coq-community} is an informal organization run by volunteer Coq users with objectives to maintain interesting Coq projects on the long-term and help Coq users to collaborate on documentation, tooling, etc.
%
It was created in 2018, inspired by the \emph{Elm Community} organization~\cite{zimmermann:tel-02451322}, and in fact such ``Community Package Maintenance Organizations'' exist in many ecosystems~\cite{zimmermann2021grounded}.
%
Today, it hosts over 50 projects maintained by over 30 maintainers.
